ZCB Pricing

### 2018-08-05 ZCB Pricing .Rmd
BOundary conditions

  # Working backwards in time
  for (i in 1:(length(I)+1)){
    Bond_values <- Diag_1%*%Bond_values
    Bond_values <- Bond_values
  }

@@

  for (i in 1:(length(I) +1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (-pu(M))*Bond_values[M,1]
    C[1,1] <- -pd(1)

    RHS <- Bond_values  # Working backwards recursively 
    Bond_values <- Inv%*%RHS
  }

@@

  # C_1 <- matrix(0,nrow = M,ncol = 1)
  # C_1[1,1] <- -2*pd(1)
  # C_1[M,1] <- -2*pu(M)
  # 
  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)
  Inv <- solve(Diag_1)

  for (i in 1:(length(I)+1)){

    RHS <- Diag_2%*%Bond_values 
    Bond_values <- Inv%*%RHS
  }

@@

for (i in 1: length(xvec)){
  Expl[i] <- explicit(r = xvec[i])
}

>>>>

  # Working backwards in time
  for (i in 1:(length(I)+1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (pu(M))*Bond_values[M,1]
    C[1,1] <- pd(1)*Bond_values[1,1]

    Bond_values <- Diag_1%*%Bond_values
    Bond_values <- Bond_values
  }

@@

  for (i in 1:(length(I) +1)){
    C <- matrix(0,ncol = 1, nrow = M) # Another matrix for boundary conditions
    C[M,1] <- (-pu(M))*Bond_values[M,1]
    C[1,1] <- -pd(1)*Bond_values[1,1]

    RHS <- Bond_values + C # Working backwards recursively 
    Bond_values <- Inv%*%RHS
  }

@@

  # C_2 <- matrix(0,nrow = M,ncol = 1)
  # C_2[1,1] <- pd(1)
  # C_2[M,1] <- pu(M)
  Inv <- solve(Diag_1)

  for (i in 1:(length(I)+1)){
    C_1 <- matrix(0,nrow = M,ncol = 1)
    C_1[1,1] <- pd(1)*Bond_values[1,1]
    C_1[M,1] <- pu(M)*Bond_values[M,1]
    RHS <- Diag_2%*%Bond_values +2*C_1
    Bond_values <- Inv%*%RHS
  }

@@

for (i in 1: length(xvec)){
  Expl[i] <- explicit(r = xvec[i], I = 1:10000)
}
